### 2025-08-10 README.Rmd
gh dl monitor

<!-- badges: start -->
[![traveltime status badge](https://idem-lab.r-universe.dev/badges/traveltime)](https://idem-lab.r-universe.dev/traveltime)
[![R-CMD-check](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml)
![GitHub License](https://img.shields.io/github/license/geryan/traveltime)
![GitHub commit activity](https://img.shields.io/github/commit-activity/w/geryan/traveltime)
![GitHub last commit](https://img.shields.io/github/last-commit/geryan/traveltime)
![GitHub commits since latest release](https://img.shields.io/github/commits-since/geryan/traveltime/latest)
[![Codecov test coverage](https://codecov.io/gh/idem-lab/traveltime/graph/badge.svg)](https://app.codecov.io/gh/idem-lab/traveltime)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](code_of_conduct.md)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![traveltime status badge](https://idem-lab.r-universe.dev/badges/traveltime)](https://idem-lab.r-universe.dev/traveltime)
[![R-CMD-check](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/idem-lab/traveltime/actions/workflows/R-CMD-check.yaml)
![GitHub License](https://img.shields.io/github/license/geryan/traveltime)
![GitHub commit activity](https://img.shields.io/github/commit-activity/w/geryan/traveltime)
![GitHub last commit](https://img.shields.io/github/last-commit/geryan/traveltime)
![GitHub commits since latest release](https://img.shields.io/github/commits-since/geryan/traveltime/latest)
[![Codecov test coverage](https://codecov.io/gh/idem-lab/traveltime/graph/badge.svg)](https://app.codecov.io/gh/idem-lab/traveltime)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](code_of_conduct.md)
![GitHub Downloads (all assets, latest release)](https://img.shields.io/github/downloads/idem-lab/traveltime/latest/total)
<!-- badges: end -->
